\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-03 paper.tex
Updated section 5

Average fixation on the reference side: The main area (right hand side
of figure 2) in the observation phase is treated as the reference side
in the interaction phase. The rationale behind keeping the lines drawn
by the robot in the observation phase is for the participants to be able
to refer to the prior behaviour of the robot in the interaction phase. We
measured the amount of time a participant looks at the reference side
and averaged this duration for the number of fixations on the reference
side for the particular participant.

@@

We measured the distances from the target for all 5 trials. As soon as the principle of the robot was deemed to be understood by the participants, almost all the participants behaved the same way. On the first try almost every participant failed and the robot turned instantly. So the most significant distance measure was the
improvement between the first and second trial. It is referred to as improvement in the next section.

@@

@@

@@

The average fixation duration on the robot during observation phase
(Figure~\ref{res1}) is significantly more in {\sf TRUE} and {\sf RANDOM} condition than in
the {\sf NONE} condition ($F[2,49]=3.68$, p = .03). This depicts that the
sensor data visualisation has an effect on the users' attention.

@@

There is a significant negative correlation between the number of
fixations on the reference side (Figure~\ref{res4}) during the interaction phase
and the first Improvement ($t(50)=-2.13$, Pearson's correlation = -0.29, p=.03).

@@

We present an exemplar eye-tracking study in the context of human-robot
interaction within an educational setting. In this section we give an example of
"how to interpret the eye-tracking results". The fact that participants have
higher average fixation duration on the robot during the observation phase in
the {\sf NONE} condition than the other two conditions (Figure 4) is not
surprising as displaying visual information on the robot induces a saliency
effect on the attention and the gaze is attracted towards the salient feature in
the field of view.

>>>>

Average fixation on the reference side: The main area (right hand side
of figure \ref{playground}) in the observation phase is treated as the reference side
in the interaction phase. The rationale behind keeping the lines drawn
by the robot in the observation phase is for the participants to be able
to refer to the prior behaviour of the robot in the interaction phase. We
measured the amount of time a participant looks at the reference side
and averaged this duration for the number of fixations on the reference
side for the particular participant.

@@

We measured the distances from the target for all 5 trials. As soon as the principle of the robot was deemed to be understood by the participants, almost all the participants behaved the same way. On the first try almost every participant failed with the robot turning instantly. So the most significant distance measure was the
improvement between the first and second trial. It is referred to as improvement in the next section.

@@

In this section, we give some of the results form the study which illustrate how fixations can be used to analyse the behaviours during the human-robot interaction and the cognitive constructs can be supported with the results.

@@

First, we show how fixation durations can be used to compare the experimental conditions and the task based performance levels.

@@

The average fixation duration on the robot during observation phase
(Figure~\ref{res1}) is significantly more in {\sf TRUE} and {\sf RANDOM} condition than in
the {\sf NONE} condition ($F[2,49]=3.68$, p = .03). This shows that the
sensor data visualisation has an effect on the users' attention.

@@

Now we show how we can use the fixation counts on different areas of interest to analyse the different task based performance levels. There is a significant negative correlation between the number of
fixations on the reference side (Figure~\ref{res4}) during the interaction phase
and the first Improvement ($t(50)=-2.13$, Pearson's correlation = -0.29, p=.03).

@@

The fact that participants have
higher average fixation duration on the robot during the observation phase in
the {\sf NONE} condition than the other two conditions (Figure 4) is not
surprising as displaying visual information on the robot induces a saliency
effect on the attention and the gaze is attracted towards the salient feature in
the field of view.
